Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-26 1_manuscript/itt-emotion_V6-4.tex
V6-4 -2165 words, changed layout of discussion

  Previous research in satisfaction has shown that different cultural backgrounds give rise to different expectations and thus different satisfaction factors. We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if services are valued over other factors in different price ranges. We compared soft attributes, such as service, with hard attributes, such as location and facilities.
  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors and then used them to classify a more extensive data set with an SVM. We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives. 
  We found that Chinese tourists are less concerned with hospitality and more with room quality, whereas, Western tourists are delighted more by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}. This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels. Both groups tend to have high expectations for the overall facilities. Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.

@@

    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels. The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms. Other mentions included big markets nearby or a big bed. Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel. However, they still reacted positively in cheaper hotels. When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel. Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).'' In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' The word ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})'' can be used bathing in the natural source of the water in rock baths or using the natural hot spring water in artificially made tiled bath facilities. It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude. It could be a cultural shock for many tourists but a fundamental attraction for many others.

    However, the size of the room or the bed is a hard attribute, of which a change is not trivial. In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings. We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples. In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair. Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers and they were mostly pleased when their expectations were fulfilled.

    A key component found in Chinese customer satisfaction soft factors was the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. This keyword was also present in all price ranges, albeit at different priorities in each of them. For this reason, we regard it as an important factor. From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings. It is only slightly lower in other categories, although it is not depicted on the table. Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase the number of good reviews.

@@

    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them. In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings. However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.

    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''; because this is an adjective, we also explored the word pairings. Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general. When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.

@@

    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes. Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night. For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns. Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains. Another common complaint was that there were no nonsmoking facilities available. The smell of smoke can completely ruin some customers’ stay and thus lead to bad reviews, thereby lowering the number of future customers.

@@

    To date, scholars have been correcting our historical bias towards the West. Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction. In other words, tourists of a particular culture have different leading satisfaction factors across different destinations. However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world. Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.

    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists. As explained earlier in this paper, Japan is well known for its customer service. Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well. The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture, and this might be unforeseen by some customers. In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.

@@

    Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors. Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high-standard hospitality environment. This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}. While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging. Chinese language pamphlets as well as Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V. channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples. Dissatisfaction in a foreign country is natural if the language native to that region is not known. \cite{ryan2001} also found that communication difficulty was one of the main reasons that Chinese customers would state for not visiting again. However, this issue is not exclusive to Japan.

@@

    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction. Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.,][]{shanka2004,choi2001}. However, hard attributes are not usually analyzed in satisfaction studies. It is important to consider both kinds of attributes. If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future. Otherwise, if the satisfaction was related more with hard attributes overall, hotels should be built considering the location while minimizing other costs. Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.

    Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors. The rates are similar for most price ranges except the highest-priced hotels, where 35 \% of the keywords are undefined. However, the soft attributes are still similar at 18 \%. However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges. Chinese tourists may expect spaciousness and cleanliness when coming to Japan. The expectation may be due to reputation, previous experiences, or cultural backgrounds. We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}. These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well. This keyword was found for hotels priced at more than 20,000 yen per night.

@@

    For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money. However, English-speaking customers complained about price less in lower-priced hotels. In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges. A study on Chinese tourists found that they had this concern \cite[][]{truong2009}. However, our results indicate that this concern is less related to the cultural attribute in Japanese hotels and more related with the pricing of hotels overall. Tourists coming to Japan could be either experienced or first-time travelers. However, their expectation of the price for hotels was lower than the actual prices in Japan. In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking. Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night. Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night. For comparison, hotels in the USA with a similar quality can charge half the price.

@@

    Western tourists are mainly dissatisfied with soft attributes. This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel. Improvement scope for Western tourists is more extensive than that for their Chinese counterparts. As such, it presents a larger investment opportunity. As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, since they spend more than 45 \% of their budget on hotel lodging.
    Asian tourists spend only 25 \% of their budget on hotels \cite[][]{choi2000}. With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell. Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment, which could increase returns by several times.

    However, Chinese customers are more in number, even though they tend to spend less on lodging. Attracting a large number of Chinese customers can be a viable strategy for hotels. However, as mentioned before, they tend to focus more on hard attributes; thus, breaking the language barrier breaking is one of the few strategies to accomplish this.

    In \cite{donthu1998cultural}, subjects from 10 different countries were compared with respect to their expectations of service quality and analyzed based on Hofstede's typology of culture \cite[][]{hofstede1984culture}. The previous study states that, although culture has no specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others. These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism–-collectivism}, \textit{masculinity–femininity}, and \textit{long-term-–short-term orientation}. In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs. collectivist countries, high uncertainty avoidance countries vs. low uncertainty avoidance countries). However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}. Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism as well as considering a difficult dimension to measure \cite[][]{fang2003critique}. Other models, such as the GLOBE model, also consider some of Hofstede's dimensions and replace them with others, making a total of nine dimensions \cite[][]{house1999cultural}. The \textit{masculinity–-femininity} dimension, for example, is proposed to be instead of two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}. This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes. Such gender stereotypes have also been the subject of critique on Hofstede's model\cite[][]{jeknic2014gender}. We agree with these critiques and thus avoid considering such stereotypes in our discussion.

    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese}. These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations. Regardless of the cause, however, measures in the past have proven that such differences exist \cite[][]{armstrong1997importance}.

    For our purposes of contrasting Western vs. Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors. The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment. Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations. However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.

    Nevertheless, a Chinese cultural attribute emphasizes that the environment and the location  affect satisfaction, rather than the treatment. According to previous research, Chinese tourists are collectivists, whereas Westerners are individualists \cite[][]{kim2000}. A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment. According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.

    Among other dimensions in both models, we can consider uncertainty avoidance. Customers of high uncertainty avoidance carefully plan their travel and thus have higher expectations towards service. In contrast, customers of lower uncertainty avoidance do not take risks in their decisions and thus face less disappointment with different expectations. However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology. While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard–-soft attribute satisfaction between Chinese and Western cultures. Differences in another factor, power distance, were also noted when measuring by Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.

@@

    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels. For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges. In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range. It is widely known in Japan that many Chinese tourists visit Japan for shopping. \cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}. Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions. Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities. Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking. In contrast, for Chinese customers, this keyword is the top keyword across all price ranges. Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.

@@

>>>>

  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for analyzing expectations and satisfaction factors in Chinese and Western cultures, our cross-cultural study contributes to both the theoretical understanding of  satisfaction and suggests practical applications and strategies for hotel managers.
  We compared soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors and then used them to classify a more extensive data set with an SVM. We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives. 
  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior. We also found that the lack of a Chinese-friendly environment for Chinese customers, and the smell of cigarettes for Western ones can be disappointing factors of their stay.

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}. However, studies focusing on only the behavior of this subset of tourists are the majority. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels. Both groups tend to have high expectations for the overall facilities. Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.

@@

    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels. The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms. Other mentions included big markets nearby or a big bed. Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel. When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel. Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).''

    In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' However, they are interchangeable if natural hot spring water is used in artificially made tiled bath facilities. It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude. It could be a cultural shock for many tourists but a fundamental attraction for many others.

    Chinese customers are satisfied with the size of the room or the bed, however it is not trivial to change this. In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings. We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples. In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair. Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers and they were mostly pleased when their expectations were fulfilled.

    A key soft satisfaction factor was the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' referring to the hotel commodities, was frequently used in positive texts compared to other food-related words across all price ranges, albeit at different priorities in each of them. For this reason, we regard it as an important factor. From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings. It is only slightly lower in other categories, although it is not depicted on the table. Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase the number of good reviews.

@@

    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the highest ranked of these three, ranking second for satisfied customers across most price ranges and only third in one of them. The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings. However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.

    Another soft attribute that is high on the list for most of the price ranges is the word ``clean'', so we examined its word pairings. Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general. When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.

@@

    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes. Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night. For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns. Tobacco was referenced singularly as ``cigarette'', but also in word pairs in Table \ref{tab:adj_en_neg} as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains. Another common complaint was that there were no nonsmoking facilities available. The smell of smoke can completely ruin some customers’ stay and thus lead to bad reviews, thereby lowering the number of future customers.

@@

    To date, scholars have been correcting our historical bias towards the West. Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction. In other words, tourists of a particular culture have different leading satisfaction factors across different destinations. However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world. Our study explores whether such an environment can affect different cultures equally or whether it is attractive only to certain cultures.

    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists. As explained earlier in this paper, Japan is well known for its customer service. Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well. The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture, and perhaps unexpected. In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.

@@

    Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors. Chinese tourists may have expectations about their treatment that are not being met, even in this high-standard hospitality environment. This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}. While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging. Chinese language pamphlets as well as Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V. channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples of these accommodations. \cite{ryan2001} also found that communication difficulty was one of the main reasons that Chinese customers would state for not visiting again. However, this issue is not exclusive to Japan.

@@

    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction \cite[e.g.,][]{shanka2004,choi2001}. Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel. However, hard attributes are not usually analyzed in satisfaction studies. It is important to consider both kinds of attributes. If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future. Otherwise, if the satisfaction was related more with hard attributes overall, hotels should be built considering the location while minimizing other costs. Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.

    Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors. The rates are similar for most price ranges except the highest-priced hotels. However, two of these soft attributes are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges. Chinese tourists may expect spaciousness and cleanliness when coming to Japan. The expectation may be due to reputation, previous experiences, or cultural backgrounds. We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}. These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well. This keyword was found for hotels priced at more than 20,000 yen per night.

@@

    For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money. However, English-speaking customers complained about price less in lower-priced hotels. In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges. A study on Chinese tourists found that they had this concern \cite[][]{truong2009}. However, our results indicate that this has more to do with the pricing of hotels in Japan overall, than with Chinese culture. In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking. Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night. Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night. For comparison, hotels in the USA with a similar quality can charge half the price.

@@

    Western tourists are mainly dissatisfied with soft attributes. This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel. Improvement scope for Western tourists is more extensive than that for their Chinese counterparts. As such, it presents a larger investment opportunity.

@@

    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels. For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges. In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range. It is widely known in Japan that many Chinese tourists visit Japan for shopping. \cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among \textit{souvenir} items representative of the culture or places that they visit \cite{japan2014consumption}. Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions. Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities compared to Chinese tourists.

    Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking. In contrast, for Chinese customers, this keyword is the top keyword across all price ranges. Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.

@@

  \subsection{Cross-culture analysis of expectations and satisfaction}\label{disc:culture}

    In \cite{donthu1998cultural}, subjects from 10 different countries were compared with respect to their expectations of service quality and analyzed based on Hofstede's typology of culture \cite[][]{hofstede1984culture}. The previous study states that, although culture has no specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others. These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism–-collectivism}, \textit{masculinity–femininity}, and \textit{long-term-–short-term orientation}. In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs. collectivist countries, high uncertainty avoidance countries vs. low uncertainty avoidance countries).

    However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}. Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism as well as considering a difficult dimension to measure \cite[][]{fang2003critique}. Other models, such as the GLOBE model, also consider some of Hofstede's dimensions and replace them with others, making a total of nine dimensions \cite[][]{house1999cultural}. The \textit{masculinity–-femininity} dimension, for example, is proposed to be instead of two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}. This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes. Such gender stereotypes have also been the subject of critique on Hofstede's model\cite[][]{jeknic2014gender}. We agree with these critiques and thus avoid considering such stereotypes in our discussion.

    For our purposes of contrasting Western vs. Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.

    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese, kim2000}. These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations. Regardless of the cause, however, measures in the past have proven that such differences exist \cite[][]{armstrong1997importance}.

    The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment. Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations. However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}. Nevertheless, one could argue a Chinese cultural attribute emphasizes that the environment and the location affect satisfaction, rather than the treatment they receive.

    A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment. According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.

    Among other dimensions in both models, we can consider uncertainty avoidance. Customers of high uncertainty avoidance carefully plan their travel and thus have higher expectations towards service. In contrast, customers of lower uncertainty avoidance do not take risks in their decisions and thus face less disappointment with different expectations. However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology. While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard–-soft attribute satisfaction between Chinese and Western cultures. Differences in another factor, power distance, were also noted when using  Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
